---
title: "EDA of Foreign Trade Statistics - Vehicle and Trailer Tracking"
output:
   html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: united
    highlight: pygments
---
```{css, echo = FALSE}
h1.title{
  color:#d3501d;
}
h3{
  color:#084a4a;
}
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# EDA of Foreign Trade Statistics

These data sources contains Export, Import and Empty Entry data of Turkish and Foreign Vehicles.

There are six data sources from the TCMB site. One of the links is given below.

[Dataset Link](https://evds2.tcmb.gov.tr/index.php?/evds/serieMarket/collapse_19/5100/DataGroup/english/bie_undnakliyetih)


## Preprocess of Foreign Trade Statistics - Vehicle and Trailer Tracking


### Import Data and Necessary Libraries

Our first step was downloading the excel data from the source and importing these files to RStudio.

Here is the code that we import and format the columns into proper data type.(There were character formatted columns which needed to be formatted into numeric.)


```{r, echo =TRUE, eval = TRUE, warning=FALSE, message=FALSE}

library(readxl) ## for importing excel files
library(tidyverse) ## for manipulating df's
library(countrycode) ## for conversion of country codes
library(dplyr) ## for data manipulation
library(kableExtra) # Pretty print DataFrame
library(zoo) # Used for converting year month character to date data type
library(wordcloud2)


df_tbg_entry <- read_excel("ProjectData/EVDS_TBG_ENTRY.xlsx")
df_tbg_entry <- df_tbg_entry %>% mutate_at(-c(1),funs(type.convert(as.numeric(.))))
df_tih_export <- read_excel("ProjectData/EVDS_TIH_EXPORT.xlsx")
df_tih_export <- df_tih_export %>% mutate_at(-c(1),funs(type.convert(as.numeric(.))))
df_tit_import <- read_excel("ProjectData/EVDS_TIT_IMPORT.xlsx") 
df_tit_import <- df_tit_import %>% mutate_at(-c(1),funs(type.convert(as.numeric(.))))
df_ybg_entry<- read_excel("ProjectData/EVDS_YBG_ENTRY.xlsx") 
df_ybg_entry <- df_ybg_entry %>% mutate_at(-c(1),funs(type.convert(as.numeric(.))))
df_yih_export<- read_excel("ProjectData/EVDS_YIH_EXPORT.xlsx") 
df_yih_export <- df_yih_export %>% mutate_at(-c(1),funs(type.convert(as.numeric(.))))
df_yit_import<- read_excel("ProjectData/EVDS_YIT_IMPORT.xlsx") 
df_yit_import <- df_yit_import %>% mutate_at(-c(1),funs(type.convert(as.numeric(.))))
```



### Changing the Names of Columns and Ordering the Columns

There are some problems with these data frames, those we had to get over:

1. There were 169 columns of each data frames. We needed to split them by countries.
2. Column names were not defined clearly, so we needed to re-define the column names. Here is one of the raw data frame column names.\

```{r}
print(head(colnames(df_tbg_entry)))
```


3. There are country codes, which is complex to read. We needed to convert country codes into country names.
4. And after we split those dataframes by countries, those were later merged into a single dataframe.

Here is the code we create a list which includes the column names those we wanted. The sequence related with raw dataframes.

```{r, echo = TRUE, eval = TRUE, warning=FALSE, warning=FALSE}
colnames_fixed = c("Level", "PercentageChange","Difference","YearlyPercentageChange","YearlyDifference","DtePreviousYearPercentageChange","DtePreviousYearPercentageDifference","MovingAverage","MovingSum")
```

Here is the two functions work nested each other. "get_country_codes" function gets the converts the country code into
country name. Split and combine uses "get_country_codes" function, and splits the main dataframe by countries as new dataframe merge all dataframes into one by their properties.(Is it foreign or Turkish vehicles or Import-Export etc.)


```{r, echo =TRUE, eval = TRUE, warning = FALSE, message=FALSE}
get_country_codes <- function(df){    
  
  country_codes <- list() 
  
  for(val in names(df))   
  {
    country_code <- strsplit(val,split=" ")[[1]][4] 
    
    if(!is.na(country_code) & !country_code %in% country_codes){
      
      country_codes <- append(country_codes,country_code)
    }
    
  }
  
  return(country_codes)
}


split_and_combine <- function(df,vehicletype,exportimport){
  
  country_codes <- get_country_codes(df)
  
  datasets <- list()
  
  for(code in country_codes){
    
    df_corrected <- df %>% select(contains(paste(" ",code," A",sep="")))
    
    colnames(df_corrected) <- colnames_fixed
    
    df_corrected$Date <- df$Tarih
    
    df_corrected$ExportImportCountry <- code
    
    df_corrected$VehicleType <- vehicletype
    
    df_corrected$ExportImport <- exportimport
    
    df_corrected$ExportImportCountry <- countrycode(df_corrected$ExportImportCountry,origin = 'iso2c', destination = 'country.name',custom_match = c('CT'='Northern Cyprus','XK' = 'Kosovo','XS'='Serbia'))
    
    datasets <- append(datasets,list(df_corrected))
    
  }
  
  return(bind_rows(datasets))
  
}
```

In this last code. We use split and combine function for all of the dataframes and we merged all of data frames those we created with "split_and_combine" function via using bind_rows function.

```{r, echo=TRUE, eval=TRUE, message=FALSE, warning= FALSE}
df_tih_export_cleaned <- split_and_combine(df_tih_export,'TIH','EXPORT')
df_yih_export_cleaned <- split_and_combine(df_yih_export,'YIH','EXPORT')

df_tit_import_cleaned <- split_and_combine(df_tit_import,'TIT','IMPORT')
df_yit_import_cleaned <- split_and_combine(df_yit_import,'YIT','IMPORT')

df_tbg_entry_cleaned <- split_and_combine(df_tbg_entry,'TBG','EMPTY ENTRY')
df_ybg_entry_cleaned <- split_and_combine(df_ybg_entry,'YBG','EMPTY ENTRY')

df_exportimport_final <- bind_rows(df_tih_export_cleaned, df_yih_export_cleaned,df_tit_import_cleaned,df_yit_import_cleaned,df_tbg_entry_cleaned,df_ybg_entry_cleaned)
df_exportimport_final[is.na(df_exportimport_final)] <- 0
df_exportimport_final$Date <- as.yearmon(df_exportimport_final$Date)

```

### Final Data Frame after Preprocess
\

Now we have the single data frame that includes all we wanted.

Here is a preview of our single data frame.

```{r chunk-name, include="FALSE"}
rm(df_tih_export)
rm(df_yih_export)
rm(df_tit_import)
rm(df_yit_import)
rm(df_tbg_entry)
rm(df_ybg_entry)
rm(df_tih_export_cleaned)
rm(df_yih_export_cleaned)
rm(df_tit_import_cleaned)
rm(df_yit_import_cleaned)
rm(df_tbg_entry_cleaned)
rm(df_ybg_entry_cleaned)
```

```{r, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
kable(tail(df_exportimport_final)) %>%
  kable_styling("striped", full_width = F) %>%
  scroll_box(width = "100%", height = "400px")
```


# Exploratory Data Analysis

In this section we will analyze and find some interesting insights from our dataset.

### Summary of Dataset

We have 13 columns. 3 of them is character data type, 1 of them is date data type and rest of all is numeric data type.

You can see detailed summary statistics from below.

```{r, echo = TRUE, eval = TRUE, warning=FALSE, warning=FALSE}

summary(df_exportimport_final)

```

### Missing Values

We don’t have any missing values in our tables as you can see below, that is because we have already fill NA values with 0 in preprocess step.

```{r, echo = TRUE, eval = TRUE, warning=FALSE, warning=FALSE}

colSums(is.na(df_exportimport_final))

```

### Most Import-Export Countries


The Word Cloud graphs in the below shows us most imported and exported countries based on country name size.

Most import countries as we can see below are EU countries such as Germany, Italy, France etc. On the other hand countries close to our border like Iraq, Iran, Bulgaria etc.


Import Plot

```{r, echo = TRUE, eval = TRUE, warning=FALSE, message=FALSE,error=FALSE}


#Import
ImportFreq <- df_exportimport_final %>% filter(ExportImport == 'IMPORT') %>% group_by(ExportImportCountry) %>% summarize(TotalImport = sum(Level)) %>% arrange(desc(TotalImport))

wordcloud2(data=ImportFreq, size=0.8)

```


Most export countries as we can see below are countries close to our borders. Top countries are usually in middle east or Asia, followed by EU countries.

Export Plot


```{r, echo = TRUE, eval = TRUE, warning=FALSE, message=FALSE,error=FALSE}


#Export
ExportFreq <- df_exportimport_final %>% filter(ExportImport == 'EXPORT') %>% group_by(ExportImportCountry) %>% summarize(TotalExport = sum(Level)) %>% arrange(desc(TotalExport))

wordcloud2(data=ExportFreq, size=0.8)

```



### Export-Import Trend

```{r, echo = TRUE, eval = TRUE, warning=FALSE, message=FALSE,error=FALSE}


df_exportimport_final %>% filter(ExportImport == 'EXPORT' | ExportImport == 'IMPORT')  %>% group_by(Date,ExportImport) %>% summarize(TotalExport = sum(Level)) %>%   ggplot( aes(x=Date, y=TotalExport, group=ExportImport, color=ExportImport)) +
         geom_line() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```


