---
output:
  xaringan::moon_reader:
    lib_dir: libs
  html_document: default
---

```{r, echo =FALSE, eval = TRUE, warning=FALSE, message=FALSE}

library(readxl) ## for importing excel files
library(tidyverse) ## for manipulating df's
library(countrycode) ## for conversion of country codes
library(dplyr) ## for data manipulation
library(kableExtra) # Pretty print DataFrame
library(zoo) # Used for converting year month character to date data type
library(wordcloud2)

df_exportimport_final <- readRDS('ProjectData/ProcessedData/df_exportimport_final.rds')

```

class: center,middle
# Foreign Trade Statistics - Vehicle and Trailer Tracking

The Wall

2021.12.07
---
# Group Project

This presentation was prepared for group project of BDA 503-Essentials Data Analytics course.

Group Members;

- Anıl Okyol
- Kerem Yalçınkaya
- Kadir Baver Kerimoğlu 
---

# Dataset Information

Foreign Trade Statistics - Vehicle and Trailer Tracking dataset includes information on Export, Import and Empty Entry data of Turkish and Foreign Vehicles from 2012 to 2021 with total 72 countries. There are total 14 attributes.

You can find the whole report in [here.](https://pjournal.github.io/mef05g-the-wall/FinalProject/EDA_ForeignTradeStatistics.html)
---

# Objectives and Project Steps

In this group project we analyzed the import and export numbers based on different attributes.


Here is the steps we've taken,

- Downloading Data
- Transforming and Cleaning Data
- Exploratory Data Analysis
- Creating a functional Shiny App that shows Import/Export Information with multiple filters given by end user.

---
# Data

```{r, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
str(df_exportimport_final)
```





